<!-- # --- -->
title: "VedicDateTime"
subtitle: "VedicDateTime Dummy Package for tests"
author: "Ajay Singh"
output: 
   rmarkdown::html_vignette
   css: !expr bslib::bs_theme(bootswatch = "cerulean", version = 5) <!--This will use the Bootstrap 5 theme-->
vignette: >
  %\VignetteIndexEntry{VedicDateTime}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```
<!--This loads the swephR package required by the VedicDateTimeSample package-->
```{r, include = FALSE}
library(swephR)
data(SE)
options(digits = 5)
```
```{r, include = FALSE}
library(VedicDateTime)
data(SE)
```
```{r setup}
library(VedicDateTimeSample)
```
\break
To calculate the magnitude of a solar eclipse at a given location:-

```{r}
jd <- 2460760.5
lat <-28.7041
long <- 77.1025
alt <- 0
magnitude_of_sol_eclipse(jd,lat,long,alt)
```

To calculate the magnitude of a lunar eclipse at a given location:-

```{r}
jd <- 2460760.5
lat <-28.7041
long <- 77.1025
alt <- 0
magnitude_of_lunar_eclipse(jd,lat,long,alt)
```

To find the Nirayana rashi:-

```{r}
jd <- 2460760.5
nirayana_rashi_name(jd)
```

To check if moon is in a waning or waing phase given gregorian date:-

```{r}
jd <- 2460760.5
is_moon_waxing(jd)
```

To calculate the planetary phase data of a planet given julian day:-

```{r}
jd_ut <- 2460760.5
planet <-1
planetary_phase_data(jd_ut,planet)
```

